Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-06-06 SDSS Presentation/SDSS Presentation.Rmd
Updates to images

- Vital Statistics (Town-centric and county level)

.column[
<img src="images/vital1.png" width="50%"/>
<img src="images/vital2.png" width="50%"/>
]

@@

+ Our feedback from users has two components:

   + User prompted (using a survey and screenshots)

   + User behaviors being record in the background:

      + This will help validate issues that are being mentioned in the survey.

      + e.g. "I'm having a hard time understanding the PCP information", we will see that users are not spending any time on the PCP.

.center[
<img src="images/feedback_question.png" width="35%"/>
]
---
class:primary

>>>>

- Vital Statistics (Town-centric and county level)
.center[
.column[
<img src="images/vital1.png" width="45%"/>
<img src="images/vital2.png" width="45%"/>
]
]

@@

+ Our feedback from users has two components:
   + User prompted (using a survey and screenshots)
   + User behaviors being record in the background:
      + This will help validate issues that are being mentioned in the survey.
      + e.g. "I'm having a hard time understanding the PCP information", we will see that users are not spending any time on the PCP.

.center[
<img src="images/feedback_question.png" width="44%"/>
]
---
class:primary
